Generating the Blueprints of Java Ecosystem

### 2015-02-22 msr.tex
putting stuff on the paper

 Maven is a build automation tool used primarily for Java projects, and it is hosted by the Apache Software Foundation\footnote{\url{http://www.apache.org/}}. To describe the software project being built, its dependencies on other libraries, and the build order Maven uses {\sc xml}. The repository contains more than 400,000 {\sc jar}s, in a variety of languages that are all using the {\sc jvm} platform as basis. These languages include Java, Clojure, Groovy, and Scala.

@@

Table~\ref{tbl:selected-metrics} presents the key metrics that exist in the dataset. Note that each tool

@@

@@

\cite{MKLGS14} \cite{KARA14}

@@

>>>>

 Maven is a build automation tool used primarily for Java projects, and it is hosted by the Apache Software Foundation~\cite{MAVEN}. To describe the software project being built, its dependencies on other libraries, and the build order Maven uses {\sc xml}. The repository contains more than 400,000 {\sc jar}s, in a variety of languages that are all using the {\sc jvm} platform as basis. These languages include Java, Clojure, Groovy, and Scala.

@@

Table~\ref{tbl:selected-metrics} presents the key metrics that are calculated and stored in the dataset. Each tool focuses on a different aspect of a software system; \textit{ckjm} focuses on object-oriented design metrics, \textit{jdepend} on

@@

Figure~\ref{fig:database-schema} illustrates the database

@@

In publication \cite{MKLGS14}, a

@@

\section{Availability}

The dataset and the source code of this publication, along with some utility scripts are available at \url{https://github.com/bkarak/data_msr2015}.
